---
title: "Step03_RasterToPointsYFFires"
output: html_document
date: "2024-11-25"
---

# Overview
Produce point shapefiles for burned areas within landscapes of interest. Each point is a landsat pixel.

# Packages
```{r}
library(terra)
library(gdalUtilities)
library(sf)
library(tidyverse)
library(ids)
library(stringi)

```

# Data

## Perimeter Shapefile Data

```{r}
YFBurn = st_read("../YF_RealPerimeters/OutputYFFires/YFFiresPerimeters.shp", "YFFiresPerimeters")%>%
  st_transform(crs = 3338)

```

## List of rasters  

```{r}

bilist <- list.files(path="../YF_RealPerimeters/OutputYFFires/Step02/",pattern='tif$', full.names = TRUE)

```

#View the raster
```{r}
bilist

```

### Name items in a list with file name

```{r}
names(bilist) <- tools::file_path_sans_ext(basename(bilist))

```

#Functions
```{r}


df_to_sf <- function(x){
  st_as_sf(x, 
           coords = c("lon","lat"),
           crs=3338)
}

```

# Map functions across list

```{r}
geousa <- function(list){ 
  purrr::map(list, rast) %>%
  purrr::map(., as.points) %>%
  purrr::map(., df_to_sf) %>% 
  map2(names(.), ~mutate(.x, FXN = .y)) %>%
  bind_rows() %>%
  st_intersection(., YFBurn) %>%
     mutate(ID1 = stri_rand_strings(n(), 9)) %>%
  st_transform(., crs = 3338)
  # mutate(ID = as.numeric(str_extract(FXN, "[0-9]+"))) 
    #dplyr::select(lat, lon, FXN, FIREYEA, ID1, geometry) %>%
}

```

# Apply Functions

```{r}
bi2 = geousa(bilist)
```

## Check and summarize and rename FXN and fireYr and select only the columns of interest 
##RID column is to create a unqiue ID within a given year in case you have to separate the GEE within a year because it is too big 
```{r}
bi2

length(unique(bi2$FXN))
length(unique(bi2$ID1))


bi2 <- bi2%>%
  dplyr::select(!ID)%>%
rename (ID = FXN,ID2 = fireYr)%>%
  group_by(ID2)%>%
  mutate(RID = row_number())%>%
  dplyr::select(ID1, ID2, lat, lon, ID, RECORDN, NAME, date, RID,geometry)

bi2$RID <- as.numeric(bi2$RID)

```

# Write to shp

```{r}
st_write(bi2, "OutputYFFires/BurnPoints.shp", driver="ESRI Shapefile", append = FALSE)
```

# Work around for step 5 (because we can't use modis to find burn date)
# Create separate csv files (that will look similar to the output from step 5 in EE) for each fire and each day that the fire lasted (will be between 1 - 3 days)

```{r}

###Medicine Lake (2005) Number of days burned: 2005-06-13
ManualDoBMedicineLake1 <- bi2%>%
  filter(NAME == "Medicine Lake")%>%
  mutate(BurnDate = 164)

st_write(ManualDoBMedicineLake1, "OutputYFFires/Step03/ManualDoBMedicineLake1.csv")

ManualDoBMedicineLake2 <- bi2%>%
  filter(NAME == "Medicine Lake")%>%
  mutate(BurnDate = 165)

st_write(ManualDoBMedicineLake2, "OutputYFFires/Step03/ManualDoBMedicineLake2.csv")


###Chloya Lakes (2006) Number of days burned: 2006-08-01
ManualDoBChloyaLakes1 <- bi2%>%
  filter(NAME == "Chloya Lakes")%>%
  mutate(BurnDate = 213)

#st_write(ManualDoBChloyaLakes1, "OutputYFFires/Step03/ManualDoBChloyaLakes1.csv")

ManualDoBChloyaLakes2 <- bi2%>%
  filter(NAME == "Chloya Lakes")%>%
  mutate(BurnDate = 214)

#st_write(ManualDoBChloyaLakes2, "OutputYFFires/Step03/ManualDoBChloyaLakes2.csv")

ManualDoBChloyaLakes3 <- bi2%>%
  filter(NAME == "Chloya Lakes")%>%
  mutate(BurnDate = 215)

#st_write(ManualDoBChloyaLakes3, "OutputYFFires/Step03/ManualDoBChloyaLakes3.csv")

###Marten Creen (2007) Number of days burned: 2007-06-06
ManualDoBMartenCreen1 <- bi2%>%
  filter(NAME == "Marten Creek")%>%
  mutate(BurnDate = 151)

#st_write(ManualDoBMartenCreen1, "OutputYFFires/Step03/ManualDoBMartenCreen1.csv")

ManualDoBMartenCreen2 <- bi2%>%
  filter(NAME == "Marten Creek")%>%
  mutate(BurnDate = 152)

#st_write(ManualDoBMartenCreen2, "OutputYFFires/Step03/ManualDoBMartenCreen2.csv")

ManualDoBMartenCreen3 <- bi2%>%
  filter(NAME == "Marten Creek")%>%
  mutate(BurnDate = 153)
#st_write(ManualDoBMartenCreen3, "OutputYFFires/Step03/ManualDoBMartenCreen3.csv")

## Chahalie (2008) Number of days burned: 2008-07-13
ManualDoBChahalie1 <- bi2%>%
  filter(NAME == "Chahalie")%>%
  mutate(BurnDate = 195)
#st_write(ManualDoBChahalie1, "OutputYFFires/Step03/ManualDoBChahalie1.csv")

ManualDoBChahalie2 <- bi2%>%
  filter(NAME == "Chahalie")%>%
  mutate(BurnDate = 196)
#st_write(ManualDoBChahalie2, "OutputYFFires/Step03/ManualDoBChahalie2.csv")


## Discovery Creek (2009) Number of days burned: 2009-07-17
ManualDoBDiscoveryCreek1 <- bi2%>%
  filter(NAME == "Discovery Creek")%>%
  mutate(BurnDate = 198)
#st_write(ManualDoBDiscoveryCreek1, "OutputYFFires/Step03/ManualDoBDiscoveryCreek1.csv")

ManualDoBDiscoveryCreek2 <- bi2%>%
  filter(NAME == "Discovery Creek")%>%
  mutate(BurnDate = 199)
#st_write(ManualDoBDiscoveryCreek2, "OutputYFFires/Step03/ManualDoBDiscoveryCreek2.csv")

ManualDoBDiscoveryCreek3 <- bi2%>%
  filter(NAME == "Discovery Creek")%>%
  mutate(BurnDate = 200)
#st_write(ManualDoBDiscoveryCreek3, "OutputYFFires/Step03/ManualDoBDiscoveryCreek3.csv")


## Vunle Lakes (2017) Number of days burned: 2017-07-08
ManualDoBVunleLakes1 <- bi2%>%
  filter(NAME == "Vunle Lakes")%>%
  mutate(BurnDate = 189)
#st_write(ManualDoBVunleLakes1, "OutputYFFires/Step03/ManualDoBVunleLakes1.csv")

ManualDoBVunleLakes2 <- bi2%>%
  filter(NAME == "Vunle Lakes")%>%
  mutate(BurnDate = 190)

#st_write(ManualDoBVunleLakes2, "OutputYFFires/Step03/ManualDoBVunleLakes2.csv")

ManualDoBVunleLakes3 <- bi2%>%
  filter(NAME == "Vunle Lakes")%>%
  mutate(BurnDate = 191)
#st_write(ManualDoBVunleLakes3, "OutputYFFires/Step03/ManualDoBVunleLakes3.csv")

## Burman Lakes (2021) Number of days burned: 2021-07-23
ManualDoBBurmanLake1 <- bi2%>%
  filter(NAME == "Burman Lake")%>%
  mutate(BurnDate = 204)

#st_write(ManualDoBBurmanLake1, "OutputYFFires/Step03/ManualDoBBurmanLake1.csv")

## Kuranakh (2022) Number of days burned: 2022-06-18
ManualDoBKuranakh1 <- bi2%>%
  filter(NAME == "Kuranakh")%>%
  mutate(BurnDate = 169)

#st_write(ManualDoBKuranakh1, "OutputYFFires/Step03/ManualDoBKuranakh1.csv")

ManualDoBKuranakh2 <- bi2%>%
  filter(NAME == "Kuranakh")%>%
  mutate(BurnDate = 170)

#st_write(ManualDoBKuranakh2, "OutputYFFires/Step03/ManualDoBKuranakh2.csv")


## Little Mosquito (2022) Number of days burned: 2022-07-24
ManualDoBLittleMosquito1 <- bi2%>%
  filter(NAME == "Little Mosquito")%>%
  mutate(BurnDate = 205)
#st_write(ManualDoBLittleMosquito1, "OutputYFFires/Step03/ManualDoBLittleMosquito1.csv")

```

