--
title: "Julian to month day year date"
author: "Anna Talucci"
date: '2022-09-28'
output: html_document
---

# Overview
Take Day of Burn day of year day and convert to YYYY-MM-DD for EE script for extracting FWI.

Input data is from Earth Engine output

# Library
```{r}
library(tidyverse)
library(sf)
library(vroom)
```


# Data
## Shapefile

```{r}
pts = st_read("OutputYFFires/BurnPoints.shp", "BurnPoints")

#all_predictors  <- read.csv("../Retraining/all_predictors_DateModification.csv")
pts1 = pts %>%
  dplyr::select(NAME, RID, geometry)

```

## DoB
# vector of data files

```{r}
f <- list.files(path = "../YF_RealPerimeters/OutputYFFires/Step03/", pattern = "*.csv", full.names = TRUE)
allData = vroom::vroom(f)
```

```{r}
allData
```
# add Date as string
```{r}
( allData1 = allData %>% 
    mutate(yyyymmdd= as.Date(BurnDate-1, origin=paste0(ID2, "-01-01")))%>% 
    mutate(ID1 = as.character(ID1))%>%
    mutate(Date = as.character(yyyymmdd)) %>%
  left_join(., pts1, by = join_by("RID", "NAME")) %>%
    st_as_sf() %>%
    rename(DOB_Ist = BurnDate, Ignition_date = date)
)

```


# Get calendar date
with quotes and separated by comma to add to GEE code.

```{r}
cat(paste0(sprintf("'%s'", sort(unique(allData1$Date))), collapse = ", "))

#cat(paste0(sprintf("'%s'", sort(unique(all_predictors$Date))), collapse = ", "))

cat(paste0(sprintf("'%s'", length(unique(allData1$Date)))))
cat(paste0(sprintf("'%s'", length(unique(allData1$NAME)))))

cat(paste0(sprintf("'%s'", length(unique(allData$NAME)))))
cat(paste0(sprintf("'%s'", length(unique(pts$NAME)))))
```

# Save pt shp file
```{r}
st_write(allData1, "../YF_RealPerimeters/OutputYFFires/DayofBurn.shp", driver="ESRI Shapefile", append = FALSE)
```
